\documentclass[landscape]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{fancyvrb}
\usepackage[stable]{footmisc}
\usepackage{multicol}
\pagestyle{empty}

\newcommand{\kbd}[1]{\colorbox{gray!10!}{\texttt{#1}}\hspace{5mm}}
\newcommand{\doctitle}{\texttt{AUC}\TeX \hspace{.25em} Cheatsheet}

\begin{document}

\hspace*{\fill}{\huge \bfseries \doctitle \hspace*{\fill}}
\vspace{2em}
  
\begin{multicols}{3}

\section*{Configuration}

An example configuration with \texttt{use-package}:
  
\begin{Verbatim}
(use-package auctex
  :defer t
  :config
  (setq TeX-auto-save t
        TeX-parse-self t
        reftex-plug-into-AUCTeX t)
  :hook (LaTeX-mode . reftex-mode))
\end{Verbatim}

\section*{Basic editing commands}

\begin{itemize}
\item \kbd{C-c C-m} Insert \textbf{m}acro \\
  Inserts a macro, prompting for options.
\item \kbd{C-c C-e} Insert \textbf{e}nvironment \\
  Inserts environment delimiters.
\item \kbd{C-c ]} Close environment \\
  Insert closing delimiter for the current environment.
\item \kbd{C-c C-s} Insert \textbf{s}ection \\
  Insert section*, prompting for label.
\item \kbd{C-c C-j} Insert item \\
  Insert next element within \texttt{itemize}.
\item \kbd{C-c \~} Math mode \\
  Use \texttt{\`} to type Greek - \textit{e.g.} \texttt{\`}\texttt{a}$\rightarrow\alpha$.
\end{itemize}


\section*{Font commands\footnote{ These commands work with marked region, and inside math mode.}}
\label{sec:font-commands}

\begin{itemize}
\item \kbd{C-c C-f C-i} \textbf{i}talic.
\item \kbd{C-c C-f C-b} \textbf{b}old.
\item \kbd{C-c C-f C-t} \textbf{t}ypewriter.
\item \kbd{C-c C-f C-t} \textbf{e}mphasis.
\item \kbd{C-c C-f C-d} \textbf{d}elete current font.
\end{itemize}

\section*{Build commands}

\begin{itemize}
\item \kbd{C-c C-c} Run \textbf{c}ommand \\
  Prompts for build command\footnote{ Check out \texttt{Clean} command}.
\item \kbd{C-c C-a} Build \textbf{a}ll \\
  Runs all commands, until exhausted (\textit{e.g.} \texttt{bibtex} multiple times). Fastest way to build and view a document.
\item \kbd{C-c C-r} Build \textbf{r}egion \\
  Compiles the text in the active region plus the preamble. Outputs to \texttt{\_region\_.pdf} by default.
\item \kbd{C-c \`} Show build errors \\
  Shows errors produced on build. Can use \texttt{next-error} and \texttt{previous-error} to
  navigate.
\end{itemize}

\section*{Reftex}

\begin{itemize}
\item \kbd{C-c =} Table of context \\
  Shows a table of context generated from the section's in the document.
\item \kbd{C-c (} Insert a new label \\
  The label is automatically generated based on context,
\item \kbd{C-c )} Insert reference\footnote{When cursor is over a reference, its context will show
    up in the echo area} \\
  First, prompts for the type of reference macro (\texttt{<RET>} for \texttt{\textbackslash ref}). \\
  Second, prompts for prefix (\texttt{sec:},\texttt{fig:},\texttt{eq:},\textit{etc}). \\
  Shows a candidate list of completions.
\item \kbd{C-c [} Insert citation.
\item \kbd{C-c \&} Jump to reference.
\end{itemize}

\end{multicols}
\end{document}